Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-09 Paperfolder/Paperfolder.Rmd
table 2 100% tab3 60% added AF

Dairy food, especially milk has been recommended to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all. For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since hazard is formally defined as the probability of the occurrence of an event at a given time point [@collett2015modelling]. Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably. However, it would still possibly be mixed up with "risk" that only contain pure meaning of "probability of an event" without redefining a point or a period of time in cross-sectional settings. For better understanding and interpretation of the findings from data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other. Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard. Accelerated failure time models are among these convenient tools that would avoid frequently unmet assumption of proportional hazard and directly show how faster/slower that one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].

@@

@@

@@

\resizebox*{\textwidth}{\dimexpr\textheight-\lineskip\relax}{%

@@

\hspace{1em}Pr(HR < 1) & - & 86.50\% & 99.90\% & 99.70\% & 93.50\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.70\% & 97.30\% & 96.10\% & 100.00\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 50.60\% & 93.70\% & 89.60\% & 99.00\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 47.20\% & 88.40\% & 86.30\% & 63.10\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 31.60\% & 79.70\% & 76.60\% & 87.60\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 28.80\% & 72.40\% & 64.40\% & 69.30\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 99.10\% & 99.90\% & 99.70\% & 99.50\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.90\% & 99.80\% & 98.90\% & 100.00\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 96.10\% & 99.10\% & 97.50\% & 99.80\%\\

@@

```{r tab3, echo=FALSE, eval=TRUE, message=FALSE}
library(knitr)
library(kableExtra)
dt <- read.csv("tab/HRAFTweibF.csv", header = T)
# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")

kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
    # collapse_rows(columns = 1, valign = "top") %>% 
    row_spec(0, bold = T) %>% 
  pack_rows("Model 0", 4, 7) %>%
  pack_rows("Model 1", 8, 11) %>%
  pack_rows("Model 2", 12, 15) %>%
    row_spec(15,  hline_after = TRUE) %>%
    pack_rows("Model 0", 17, 20) %>%
  pack_rows("Model 1", 21, 24) %>%
  pack_rows("Model 2", 25, 28) %>%
      row_spec(28,  hline_after = TRUE) %>%
  pack_rows("Model 0", 30, 33) %>%
  pack_rows("Model 1", 34, 37) %>%
  pack_rows("Model 2", 38, 41) %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 7) %>%
  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.")) 
```

>>>>

Dairy food, especially milk has been recommended to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all. For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since hazard is formally defined as the probability of the occurrence of an event at a given time point [@collett2015modelling]. Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably. However, it would still possibly be mixed up with "risk" that only contain pure meaning of "probability of an event" without redefining a point or a period of time in cross-sectional settings. For better understanding and interpretation of the findings from data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other. Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard to be met. Accelerated failure time models are among these convenient tools that would avoid worrying about the assumption of proportional hazard and directly show how faster/slower that one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].

@@

<!-- - summary of the finding -->

@@

-

@@

\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%

@@

\hspace{1em}Pr(HR < 1) & - & 86.5\% & 99.9\% & 99.7\% & 93.5\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.7\% & 97.3\% & 96.1\% & 100.0\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 50.6\% & 93.7\% & 89.6\% & 99.0\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 47.2\% & 88.4\% & 86.3\% & 63.1\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 31.6\% & 79.7\% & 76.6\% & 87.6\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 28.8\% & 72.4\% & 64.4\% & 69.3\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 99.1\% & 99.9\% & 99.7\% & 99.5\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 96.9\% & 99.8\% & 98.9\% & 100.0\%\\

@@

\hspace{1em}Pr(HR < 1) & - & 96.1\% & 99.1\% & 97.5\% & 99.8\%\\

@@

```{r tab3, echo=FALSE, eval=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
dt <- read.csv("tab/HRAFTweibF.csv", header = T)
# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")

kable(dt, format = "latex", caption = "Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).", booktabs = T, linesep = "", align = "lccccc") %>%
    # collapse_rows(columns = 1, valign = "top") %>% 
  row_spec(0, bold = T) %>% 
    # collapse_rows(columns = 1, valign = "top") %>% 
    pack_rows("Model 0", 4, 8) %>%
  pack_rows("Model 1", 9, 13) %>%
  pack_rows("Model 2", 14, 18) %>%
  row_spec(18,  hline_after = TRUE) %>%
  pack_rows("Model 0", 20, 24) %>%
  pack_rows("Model 1", 25, 29) %>%
  pack_rows("Model 2", 30, 34) %>%
  row_spec(34,  hline_after = TRUE) %>%
  pack_rows("Model 0", 36, 40) %>%
  pack_rows("Model 1", 41, 45) %>%
  pack_rows("Model 2", 46, 50) %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 7) %>%
  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.", "Model 0 = Crude model; Model 1 = age-adjusted model; Model 2 = multivariable adjusted model.", "Covariates included in Model 2: age, smoking habit, alcohol intake, body mass index, history of",  "hypertension, diabetes, kidney/liver diseases, exercise, sleep duration, coffee intake, education level.")) 
```

\caption{\label{tab:tab3}Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).}
\fontsize{7}{9}\selectfont
\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%
\rowcolor{gray!6}  Person-year & 173222 & 59904 & 129233 & 139919 & 418925\\
N & 10407 & 3640 & 7590 & 8108 & 25254\\
\rowcolor{gray!6}  Total Stroke & 300 & 84 & 182 & 172 & 585\\
\hspace{1em}Mean AF (SD) & 1 & 0.88 (0.07) & 0.87 (0.05) & 0.79 (0.05) & 0.88 (0.04)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.03) & (0.78, 0.98) & (0.71, 0.90) & (0.80, 0.96)\\
\hspace{1em}Mean HR (SD) & 1 & 0.83 (0.10) & 0.81 (0.08) & 0.70 (0.07) & 0.81 (0.07)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.64, 1.05) & (0.68, 0.97) & (0.58, 0.85) & (0.71, 0.93)\\
\hspace{1em}Pr(HR < 1) & - & 94.6\% & 98.7\% & 99.9\% & 99.6\%\\
\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.09) & 1.11 (0.08) & 1.02 (0.08) & 0.95 (0.06)\\
\hspace{1em}95\% CrI & - & (0.85, 1.17) & (0.97, 1.26) & (0.89, 1.16) & (0.86, 1.06)\\
\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.00 (0.14) & 1.18 (0.14) & 1.03 (0.12) & 0.92 (0.09)\\
\hspace{1em}95\% CrI & - & (0.76, 1.31) & (0.95, 1.47) & (0.82, 1.28) & (0.78, 1.09)\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 52.3\% & 6.3\% & 42.0\% & 86.8\%\\
\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.12) & 1.11 (0.14) & 1.02 (0.12) & 0.97 (0.09)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.85, 1.20) & (0.97, 1.30) & (0.89, 1.19) & (0.88, 1.10)\\
\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.17) & 1.19 (0.15) & 1.03 (0.15) & 0.95 (0.12)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.36) & (0.96, 1.52) & (0.81, 1.31) & (0.80, 1.17)\\
\hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\
\rowcolor{gray!6}  Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\
\hspace{1em}Mean AF (SD) & 1 & 0.78 (0.13) & 0.98 (0.12) & 0.90 (0.11) & 0.92 (0.09)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.55, 1.06) & (0.76, 1.25) & (0.70, 1.13) & (0.76, 1.12)\\
\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\
\hspace{1em}Pr(HR < 1) & - & 94.7\% & 58.1\% & 83.1\% & 83.0\%\\
\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.88 (0.13) & 1.12 (0.13) & 1.04 (0.13) & 0.95 (0.09)\\
\hspace{1em}95\% CrI & - & (0.63, 1.17) & (0.90, 1.41) & (0.82, 1.32) & (0.80, 1.14)\\
\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\
\hspace{1em}95\% CrI & - & (0.54, 1.24) & (0.86, 1.58) & (0.76, 1.45) & (0.73, 1.19)\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\
\hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{2} & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{2} & \\
\hspace{1em}Mean HR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\
\hspace{1em}Pr(HR < 1) & - & 79.6\% & 12.7\% & 33.4\% & 71.4\%\\
\rowcolor{gray!6}  Cerebral infarction & 102 & 35 & 63 & 50 & 187\\
\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.13) & 0.90 (0.09) & 0.75 (0.08) & 0.86 (0.06)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.27) & (0.75, 1.10) & (0.60, 0.91) & (0.75, 0.99)\\
\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.20) & 0.85 (0.14) & 0.61 (0.11) & 0.78 (0.10)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.69, 1.48) & (0.60, 1.13) & (0.43, 0.84) & (0.59, 0.99)\\
\hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\
\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{1} & \\
\hspace{1em}95\% CrI & - &  &  &  \vphantom{1} & \\
\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
\hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 36.7\% & 42.1\% & 78.7\% & 88.9\%\\
\hspace{1em}Mean AF (SD) & 1 &  &  &  & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  & \\
\hspace{1em}Mean HR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.92) & (0.86, 1.63) & (0.62, 1.23) & (0.72, 1.19)\\
\hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\

### 2020-07-09 Paperfolder/Paperfolder.tex
table 2 100% tab3 60% added AF

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Dairy food, especially milk has been recommended to reduce stroke risk
by nearly 7\% for each 200 g increment of daily consumption
\citep{DeGoede2016}. More intuitive interpretation for a decreasing risk
would be possible if we were able to compute the exact probability for
people who had milk intake may had lower hazard of dying from stroke
compared with those who never drank milk at all. For general
public/media reporting, concept of hazard in epidemiological studies
could still sometimes be challenging to be understood or misinterpreted
since hazard is formally defined as the probability of the occurrence of
an event at a given time point \citep{collett2015modelling}. Usually,
authors of epidemiological papers would tend to use ``risk'' instead of
``hazard'' or interchangeably. However, it would still possibly be mixed
up with ``risk'' that only contain pure meaning of ``probability of an
event'' without redefining a point or a period of time in
cross-sectional settings. For better understanding and interpretation of
the findings from data that researchers endeavored to collect,
statistical literature have provided plenty of choices that could help
us better communicate with each other. Another approach of comparing the
time-to-event survival probabilities between different groups would be
to model the time before observing an event rather than the hazard which
always required the assumption of a proportional hazard. Accelerated
failure time models are among these convenient tools that would avoid
frequently unmet assumption of proportional hazard and directly show how
faster/slower that one individual in an exposure group might have an
event compared to others among different exposure groups
\citep{Wei1992}.

@@

\caption{\label{tab:tab3}Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).}

@@

@@

\hspace{1em}MeanHR (SD) & 1 & 0.83 (0.10) & 0.81 (0.08) & 0.70 (0.07) & 0.81 (0.07)\\

@@

\hspace{1em}MCSE & - & 0.0029 & 0.0022 & 0.0021 & 0.0023\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 94.6\% & 98.7\% & 99.9\% & 99.6\%\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.00 (0.14) & 1.18 (0.14) & 1.03 (0.12) & 0.92 (0.09)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.76, 1.31) & (0.95, 1.47) & (0.82, 1.28) & (0.78, 1.09)\\
\hspace{1em}MCSE & - & 0.0038 & 0.0045 & 0.0042 & 0.0034\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.17) & 1.19 (0.15) & 1.03 (0.15) & 0.95 (0.12)\\

@@

\hspace{1em}MCSE & - & 0.0083 & 0.0096 & 0.0079 & 0.0075\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\

@@

Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
\hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\
\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0058 & 0.0071 & 0.0061 & 0.0065\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\

@@

\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0065 & 0.0089 & 0.0084 & 0.0069\\
\hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\

@@

\rowcolor{gray!6}  \hspace{1em}MeanHR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
\hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\
\rowcolor{gray!6}  \hspace{1em}MCSE & - & 0.0051 & 0.0067 & 0.0039 & 0.0047\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.01 (0.13) & 0.82 (0.14) & 0.59 (0.14) & 0.76 (0.16)\\

@@

\hspace{1em}MCSE & - & 0.0087 & 0.0079 & 0.0064 & 0.0071\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\
\hspace{1em}MCSE & - & 0.0071 & 0.0072 & 0.0095 & 0.0054\\

@@

\hspace{1em}MeanHR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\

@@

\hspace{1em}MCSE & - & 0.0055 & 0.0057 & 0.0067 & 0.0047\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\

@@

\end{tabular}

>>>>

\usepackage{graphicx}

@@

Dairy food, especially milk has been recommended to reduce stroke risk
by nearly 7\% for each 200 g increment of daily consumption
\citep{DeGoede2016}. More intuitive interpretation for a decreasing risk
would be possible if we were able to compute the exact probability for
people who had milk intake may had lower hazard of dying from stroke
compared with those who never drank milk at all. For general
public/media reporting, concept of hazard in epidemiological studies
could still sometimes be challenging to be understood or misinterpreted
since hazard is formally defined as the probability of the occurrence of
an event at a given time point \citep{collett2015modelling}. Usually,
authors of epidemiological papers would tend to use ``risk'' instead of
``hazard'' or interchangeably. However, it would still possibly be mixed
up with ``risk'' that only contain pure meaning of ``probability of an
event'' without redefining a point or a period of time in
cross-sectional settings. For better understanding and interpretation of
the findings from data that researchers endeavored to collect,
statistical literature have provided plenty of choices that could help
us better communicate with each other. Another approach of comparing the
time-to-event survival probabilities between different groups would be
to model the time before observing an event rather than the hazard which
always required the assumption of a proportional hazard to be met.
Accelerated failure time models are among these convenient tools that
would avoid worrying about the assumption of proportional hazard and
directly show how faster/slower that one individual in an exposure group
might have an event compared to others among different exposure groups
\citep{Wei1992}.

@@

\caption{\label{tab:tab3}Summary of posterior Acceleration Factors (AF) and Hazard Ratios (HR) of mortality from total stroke, stroke type according to the frequency of milk intake in women (JACC study, 1988-2009).}

@@

\resizebox*{!}{\dimexpr\textheight-\lineskip\relax}{%

@@

\hspace{1em}Mean AF (SD) & 1 & 0.88 (0.07) & 0.87 (0.05) & 0.79 (0.05) & 0.88 (0.04)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.75, 1.03) & (0.78, 0.98) & (0.71, 0.90) & (0.80, 0.96)\\
\hspace{1em}Mean HR (SD) & 1 & 0.83 (0.10) & 0.81 (0.08) & 0.70 (0.07) & 0.81 (0.07)\\

@@

\hspace{1em}Pr(HR < 1) & - & 94.6\% & 98.7\% & 99.9\% & 99.6\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.99 (0.09) & 1.11 (0.08) & 1.02 (0.08) & 0.95 (0.06)\\
\hspace{1em}95\% CrI & - & (0.85, 1.17) & (0.97, 1.26) & (0.89, 1.16) & (0.86, 1.06)\\
\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.00 (0.14) & 1.18 (0.14) & 1.03 (0.12) & 0.92 (0.09)\\
\hspace{1em}95\% CrI & - & (0.76, 1.31) & (0.95, 1.47) & (0.82, 1.28) & (0.78, 1.09)\\

@@

\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.12) & 1.11 (0.14) & 1.02 (0.12) & 0.97 (0.09)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.85, 1.20) & (0.97, 1.30) & (0.89, 1.19) & (0.88, 1.10)\\
\hspace{1em}Mean HR (SD) & 1 & 1.01 (0.17) & 1.19 (0.15) & 1.03 (0.15) & 0.95 (0.12)\\

@@

\hspace{1em}Pr(HR < 1) & - & 52.8\% & 6.4\% & 44.4\% & 78.0\%\\

@@

\rowcolor{gray!6}  Hemorrhagic stroke & 108 & 27 & 78 & 76 & 231\\

@@

\hspace{1em}Mean AF (SD) & 1 & 0.78 (0.13) & 0.98 (0.12) & 0.90 (0.11) & 0.92 (0.09)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.55, 1.06) & (0.76, 1.25) & (0.70, 1.13) & (0.76, 1.12)\\
\hspace{1em}Mean HR (SD) & 1 & 0.73 (0.16) & 0.98 (0.15) & 0.87 (0.14) & 0.89 (0.11)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.47, 1.08) & (0.71, 1.31) & (0.64, 1.16) & (0.71, 1.15)\\

@@

\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 & 0.88 (0.13) & 1.12 (0.13) & 1.04 (0.13) & 0.95 (0.09)\\
\hspace{1em}95\% CrI & - & (0.63, 1.17) & (0.90, 1.41) & (0.82, 1.32) & (0.80, 1.14)\\
\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 0.84 (0.18) & 1.17 (0.18) & 1.06 (0.17) & 0.93 (0.12)\\

@@

\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 81.6\% & 16.9\% & 38.9\% & 74.6\%\\

@@

\hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{2} & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  \vphantom{2} & \\
\hspace{1em}Mean HR (SD) & 1 & 0.85 (0.18) & 1.21 (0.18) & 1.13 (0.17) & 1.03 (0.12)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.56, 1.30) & (0.90, 1.62) & (0.84, 1.52) & (0.81, 1.29)\\

@@

\hspace{1em}Mean AF (SD) & 1 & 1.01 (0.13) & 0.90 (0.09) & 0.75 (0.08) & 0.86 (0.06)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.27) & (0.75, 1.10) & (0.60, 0.91) & (0.75, 0.99)\\
\hspace{1em}Mean HR (SD) & 1 & 1.03 (0.20) & 0.85 (0.14) & 0.61 (0.11) & 0.78 (0.10)\\

@@

\hspace{1em}Pr(HR < 1) & - & 51.9\% & 75.6\% & 97.6\% & 96.1\%\\

@@

\rowcolor{gray!6}  \hspace{1em}Mean AF (SD) & 1 &  &  &  \vphantom{1} & \\
\hspace{1em}95\% CrI & - &  &  &  \vphantom{1} & \\
\rowcolor{gray!6}  \hspace{1em}Mean HR (SD) & 1 & 1.29 (0.14) & 1.15 (0.13) & 0.86 (0.14) & 0.86 (0.15)\\
\hspace{1em}95\% CrI & - & (0.88, 1.89) & (0.84, 1.58) & (0.61, 1.20) & (0.67, 1.09)\\

@@

\hspace{1em}Mean AF (SD) & 1 &  &  &  & \\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - &  &  &  & \\
\hspace{1em}Mean HR (SD) & 1 & 1.30 (0.11) & 1.18 (0.09) & 0.87 (0.10) & 0.93 (0.07)\\

@@

\hspace{1em}Pr(HR < 1) & - & 35.1\% & 39.9\% & 75.6\% & 80.1\%\\

@@
